### 2020-08-27 TCS_v3/AnswerToReviewer.txt

p.8, l.13, (Res) rule - make sure all a's have same font as it seems the one in (\nu a)P' is different
> OK. Done

p.8, l.30 - replace "Fig.1" by "Fig. 1"
> OK. Done

p.12, l.35 (item 2 of Lemma 12) - replace "for each reaction" by "each reaction"
> OK. We have corrected the formulation.

p.12, l.51 - in Def. 13 shouldn't be P \xrightarrow{(\nu names)v} P' instead of P \xrightarrow{v}P' ?  Only starting on p.15, l.52 you say "In this section, for simplicity, we shall often omit topmost restrictions (\nu names)". Thus, either move this assumption earlier or till Section 5 keep using (\nu names) on \xrightarrow
>  No, Def.13 is correct: you can imagine that P contains no restrictions and therefore P \xrightarrow{v}P' is such that all the names in v are visible. Then (\nu names)P \xrightarrow{(\nu names)v} (\nu names)P' but in the label (\nu names)v all the names are transformed to silent actions \tau.

p.13, l.56 - (\nu names) missing from \xrightarrow label
>  No, see above.

@@

p.17, l.49 - replace "(starting at cxt and ending at p1" by "(starting at cxt and ending at p1)", namely add missing bracket
> OK. Done

p.33, l.41 - shouldn't be "j \geq 1" (as assumed on p.33, l.38) instead of "j \geq 0"?
> OK. Done

p.33, l.47 and l.49 - in the proof of the base case "j=1", instead of "j-1" shouldn't be "j"? This is due to the fact that Prop. 16 you mention you have the case j=1 and also on p.33 on l.52 you got \gamma^j and not \gamma^{j-1}.
>  We imagine you meant "in the proof of the inductive case". Yuo are right, we have slightly expanded the proof to make it clear the application of the inductive hypothesis.

### 2020-08-27 TCS_v3/09-appendix.tex
cambi vari
ringraziamenti progetti e indice j nella prova

% \begin{corollary}[correcteness2]
% %\label{prop:correctness2}
%  Let $P$ a  c\CNA process such that exists a rs ${\cal A}$ and a $n$-step  interactive process $\pi=(\gamma,\delta)$ with $\gamma =C_0,\dots,C_n$ and $\delta = D_0,\dots,D_n$ such that $P= [|{\cal A},\gamma|]$. 
% %We set $\pi'=(\gamma',\delta')$ with $\gamma'=C_0',\dots,C_{n-1}'$,  $\delta'=D_0',\dots,D_{n-1}$,  where $C_0'= C_1 \cup D_1$, $C_i'= C_{i+1}$, $D_i=D_{i+1}'$,  and $1 \leq i < n$.
%Then,   $\exists$ $P''$ and $\pi''=(\gamma'',\delta'')$ such that $P \xrightarrow{\link{\silent}{\silent}}^{w-1}P''$, $P'' =[|{\cal A},\gamma''|]$.
%%such that $P=[|{\cal A}|]$, then if $P \rightarrow^* P'$, then $\exists$ ${\cal A'}$ such that ${\cal A}$  evolves in ${\cal A'}$ and $P'=[|{\cal A'}|]$.
% \end{corollary}
\begin{proof}
We proceed by induction on the transition number $j \geq 0$.
% case $j=0$\\
% It is enough to set $C_0' = C_0 \cup D_0$ and $P' =P$.\\
\begin{description}
\item[base case $j=1$:]
 This case falls into the case of Proposition~\ref{prop:corr1}.
\item[inductive case:]
We assume, by inductive hypothesis, that $\exists P'$ such that 
$$P \xrightarrow{\link{\silent}{\silent}\dots \link{\silent}{\silent}}^{j-1} P'$$ 
and $P' = \llbracket{\cal A},\gamma^{j-1}\rrbracket$.
%, with $1 \leq  i < t-1$.\\
As $P'$ is the encoding of an extended interactive process, by Proposition~\ref{prop:corr1}, it exists $P''$  such that $P' \xrightarrow{\link{\silent}{\silent}\dots\link{\silent}{\silent}} P''$,
 and $P'' = \llbracket{\cal A},\gamma^j\rrbracket$. 
% By Lemma~\ref{lem:compl2}.2, if $\exists$ $P'$ such that $P'' \xrightarrow{\link{\silent}{\silent}} P'$, then $P'$ is 
 %unique, and by Lemma~\ref{lem:compl2}.1 $P' = [|{\cal A},\gamma'|]$. 
%By Proposition~\ref{prop:corr1}, we know that  $C_0''=C_1' \cup D_1'$, $C_i''= C_{i+1}'$,
% and $D_i'' = D_{i+1}'$.  And we are done, as $C_0''=C_1' \cup D_1' = C_j \cup D_j$, $C_i''= C_{i+1}' = C_{i+j}$,  and $D_i'' = D_{i+1}'= D_{i+j}$.
\end{description}
\end{proof}

>>>>

% \begin{corollary}[correcteness2]
% %\label{prop:correctness2}
%  Let $P$ a  c\CNA process such that exists a rs ${\cal A}$ and a $n$-step  interactive process $\pi=(\gamma,\delta)$ with $\gamma =C_0,\dots,C_n$ and $\delta = D_0,\dots,D_n$ such that $P= [|{\cal A},\gamma|]$. 
% %We set $\pi'=(\gamma',\delta')$ with $\gamma'=C_0',\dots,C_{n-1}'$,  $\delta'=D_0',\dots,D_{n-1}$,  where $C_0'= C_1 \cup D_1$, $C_i'= C_{i+1}$, $D_i=D_{i+1}'$,  and $1 \leq i < n$.
%Then,   $\exists$ $P''$ and $\pi''=(\gamma'',\delta'')$ such that $P \xrightarrow{\link{\silent}{\silent}}^{w-1}P''$, $P'' =[|{\cal A},\gamma''|]$.
%%such that $P=[|{\cal A}|]$, then if $P \rightarrow^* P'$, then $\exists$ ${\cal A'}$ such that ${\cal A}$  evolves in ${\cal A'}$ and $P'=[|{\cal A'}|]$.
% \end{corollary}
\begin{proof}
We proceed by induction on the transition number $j \geq 1$.
% case $j=0$\\
% It is enough to set $C_0' = C_0 \cup D_0$ and $P' =P$.\\
\begin{description}
\item[base case $j=1$:]
 This case falls into the case of Proposition~\ref{prop:corr1}.
\item[inductive case:]
We assume that the property holds for some generic $j\geq 1$ and we prove that it holds for $j+1$.
Suppose that
$$P \xrightarrow{\link{\silent}{\silent}\dots \link{\silent}{\silent}}^{j+1} P'' .$$
Then, it must exist $P'$ such that 
$$P \xrightarrow{\link{\silent}{\silent}\dots \link{\silent}{\silent}}^{j} P' \xrightarrow{\link{\silent}{\silent}\dots \link{\silent}{\silent}} P'' .$$ 
By inductive hypothesis, $P' = \llbracket{\cal A},\gamma^{j}\rrbracket$.
%, with $1 \leq  i < t-1$.\\
As $P'$ is the encoding of an extended interactive process, by Proposition~\ref{prop:corr1},  $P'' = \llbracket{\cal A},(\gamma^j)^1\rrbracket =\llbracket{\cal A},\gamma^{j+1}\rrbracket $. 
% By Lemma~\ref{lem:compl2}.2, if $\exists$ $P'$ such that $P'' \xrightarrow{\link{\silent}{\silent}} P'$, then $P'$ is 
 %unique, and by Lemma~\ref{lem:compl2}.1 $P' = [|{\cal A},\gamma'|]$. 
%By Proposition~\ref{prop:corr1}, we know that  $C_0''=C_1' \cup D_1'$, $C_i''= C_{i+1}'$,
% and $D_i'' = D_{i+1}'$.  And we are done, as $C_0''=C_1' \cup D_1' = C_j \cup D_j$, $C_i''= C_{i+1}' = C_{i+j}$,  and $D_i'' = D_{i+1}'= D_{i+j}$.
\end{description}
\end{proof}
